Unsupervised Detection and Tracking of Multiple Objects with Dependent Dirichlet Process Mixtures

### 2012-02-01 ltx/paper_brainstorm.tex
re did format of whole paper. IMPORTANT: the next .tex file of interest is: paper_short.tex

\documentclass[smallcondensed, final]{svjour3}
% \documentclass[smallcondensed, final]{svjour3}[1/1/2012]
\usepackage[square,numbers]{natbib}
\usepackage{amsmath, epsfig}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{easybmat}
\usepackage{footmisc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{subfig}
\renewcommand\algorithmiccomment[1]{// \textit{#1}}
\newcommand{\ignore}[1]{}
\newcommand{\comment}[1]{}
\newcommand{\frank}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}}
\newcommand{\willie}[1]{\textcolor{green}{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

We define the task of automated detection and tracking of arbitrary objects in videos to be the fulfillment of three actions: determining the spatiotemporal regions of a video that constitute objects (`extraction'), finding the positions and/or shapes of distinct objects (`localization'), and maintaining the identities of the detected objects over time (`tracking'). An ability to carry out these tasks in an automated manner is useful for many fields that make use of video data, including robotics, video surveillance, time-lapse microscopy, and video summarization. Algorithms able to be applied to a variety of objects and video types are particularly desirable. This paper serves to introduce a new technique involving the use of dependent Dirichlet processes mixture models, which we hope will provide the foundation for a class of unsupervised algorithms that can detect and track arbitrary objects in a wide range of videos.

>>>>

\documentclass[twocolumn, final]{svjour3}
% \documentclass[smallcondensed, final]{svjour3}[1/1/2012]
\usepackage[square,numbers]{natbib}
\usepackage{amsmath, epsfig}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{easybmat}
\usepackage{footmisc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{subfig}
\renewcommand\algorithmiccomment[1]{// \textit{#1}}
\newcommand{\ignore}[1]{}
\newcommand{\comment}[1]{}
\newcommand{\frank}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}}
\newcommand{\willie}[1]{\textcolor{green}{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

We define the task of automated detection and tracking of arbitrary objects in videos to \willie{consist of three actions} be the fulfillment of three actions: determining the spatiotemporal regions of a video that constitute objects (`extraction'), finding the positions and/or shapes of distinct objects (`localization'), and maintaining the identities of the detected objects over time (`tracking'). An ability to carry out these tasks in an automated manner is useful for many fields that make use of video data, including robotics, video surveillance, time-lapse microscopy, and video summarization. Algorithms able to be applied to a variety of objects and video types are particularly desirable. This paper \willie{introduces a new framework involving the use of dependent Dirichlet process mixture models. This framework provides the foundation for a class of unsupervised algorithms that can detect and track arbitrary objects in a wide range of videos.} 
% serves to introduce a new technique involving the use of dependent Dirichlet process mixture models, which we hope will provide the foundation for a class of unsupervised algorithms that can detect and track arbitrary objects in a wide range of videos.
